A Fully Decentralized Infrastructure for Automated and Trusted IoT Data Trading

### 2020-06-04 paper.tex

\section{Related Work}
\label{section:relatedWork}
% pub/sub
\subsection{Data exchange mechanism for IoT}
The publish/subscribe service model consists of publishers, subscribers and brokers, which has been proven\cite{pubSubAnalysis, pubSubAnalysis2} to be an efficient and flexible solution for a large number of diverse entities like IoT applications. A lot of work in publish/subscribe system focused on the scalability and the different security issues such as, encrypted data communication, privacy preserving data subscription and access control of digital asset. A few work targets on the storage which is a vital considerations for IoT and mobile computing and the incentive for data economics.

M. B. Abdullahi and G. Wang\cite{centralPubSub} presented a secure publish/subscribe data storage service in Wireless sensor networks (WSNs) which ensures several security issues. Each user has an identity for authentication, whereas subscribers' interests are encoded before matching to protect users' interests. Additionally, the proposed encryption scheme can prevent adversary to access published data if the sensor node is compromised. However, the access control and encryption keys of data is enforced by the network controllers (NCs) and Cirtificate Authorities (CAs), which may be a potential security risk of the system. Also the storage is not well illustrated in the work. G. S. Ramachandran et al.\cite{trinity} pointed out the security risk of centralized brokers, and applied DLTs to build a distributed pub/sub system which promotes the transparency of interactions of participants and the status of data. With the help of Smart Contract, usesrs can perform data validation easily, and brokers can keep track of data status. But data is plaintext on blockchain, which the privacy problem of sensitive data need to be considered carefully. The economics incentives that can encourage the publishers to participate the system and pay more attention on the quality control are not included.

@@

\subsection{Trusted IoT Trading Infrastructure}
Multiple infrastructures of trusted data marketplace for IoT data trading has been proposed. Paolo Missier et. al\cite{MindMyValue} presented an IoT brokered infrastructure based marketplace which enables the trading with Ethereum smart contracts. The brokers are only responsible for data transmission but matching publishers and subscribers as standard pub/sub model in order to adapt flexible agreement between participants. However, the data cubes (i.e., a tuple of information, such as provider, subscriber and time period) are stored in a centralized Cassandra NoSQL database, referring as TrackerDB, is guarateed to be tamperproof but the risk of single point failure still exists.

\cite{TrustedMarketplaceWearable} focuses on trading the sensitive data among wearables. Several security issues are well discussed and solved with DLTs in the paper, the system consists multiple components that has its own responsibility, such as data anonymizer eliminates keen information for privacy protection, access controller handles the key management and contract manager manages Ethereum smart contracts. While the trading processes are splited into multiple servers, and the request/response communication model is applied, the scalability problem of the marketplace remains.
% TODO:補一個 MAM 訂閱未來資料的敘述

In \cite{IOTASensorNode}, sensor nodes (SNs) in distributed sensor node system upload data to IOTA network via MAM protocol, and the Back-End server helps SNs to accelerate transaction attachments. The Back-End server also manages keys of data streams, record a tuple of SN, SN metadata, keys and available data stream entry points on MAM, and evaluates data price according to it's quality. Furthermore, as the Back-End server keeps all information of data products, it operates an user friendly interface of the marketplace and tackles all trading procedures. The Back-End server encounters the system scalability problem, single point failure as well as malicious attacks which may damage the profits of all players.

A similar approach to the previous one, the IOTA-based decentralized data marketplace in \cite{DDMSmartCities} puts data streams on the Tangle via MAM protocol as well. Yet the data marketplace does not exist any intermediate server but data providers only, data providers generate and send data streams to MAM channel, and add a specific tag in transactions as an index that the marketplace application can retreive and show the product information on a map where data consumers can select from. Payments are in IOTA token with the transaction contains another type of tag, which both providers and consumers can double-check. Once the participants grows rapidly, this searching specific transactions by tags approach may fail due to the massive amount of transactions returned. Moreover, it is difficult to filter out the interested information.

Two technical architectures for data trading are directly relevant to our work.
\cite{SocialGood} proposed a smart transportation system that incorporate two DLTs, IOTA and Ethereum and a distributed storage IPFS. Though IOTA provides better scalability, it does not provide distributed computation as Ethereum smart contract. Thus, in this approach, IOTA and Ethereum are adopted to build a secure and smart system application, which is the principle we followed in our approach. Meanwhile, IPFS and MAM are viewed as the data storage in the system, where IPFS stores data that are not convenient to store on public chain and referenced to its hash into MAM transactions. Three types of MAM channels are used interactively to minimize the channel ID and key that data producers need to manage. The access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from. Also, the details of trading are not illustrated in this paper.

>>>>

\section{Related Work}
\label{section:relatedWork}
% pub/sub
\subsection{Data exchange mechanism for IoT}
The publish/subscribe service model consists of publishers, subscribers and brokers, which has been proven\cite{pubSubAnalysis, pubSubAnalysis2} to be an efficient and flexible solution for a large number of diverse entities like IoT applications. A lot of work in publish/subscribe system focused on the scalability and the different security issues such as, encrypted data communication, privacy preserving data subscription and access control of digital asset. A few work targets on the storage which is a vital consideration for IoT and mobile computing and the incentive for data economics.

M. B. Abdullahi and G. Wang\cite{centralPubSub} presented a secure publish/subscribe data storage service in Wireless sensor networks (WSNs) which ensures several security issues. Each user has an identity for authentication, whereas subscribers' interests are encoded before matching to protect users' interests. Additionally, the proposed encryption scheme can prevent adversary to access published data if the sensor node is compromised. However, the access control and encryption keys of data is enforced by the network controllers (NCs) and Cirtificate Authorities (CAs), which may be a potential security risk of the system. Also the storage is not well illustrated in the work. G. S. Ramachandran et al.\cite{trinity} pointed out the security risk of centralized brokers, and applied DLTs to build a distributed pub/sub system which promotes the transparency of interactions of participants and the status of data. With the help of Ethereum smart contract, usesrs can perform data validation easily, and brokers can keep track of data status. But data is plaintext on blockchain, which the privacy problem of sensitive data need to be considered carefully. The economics incentives that can encourage the publishers to participate the system and pay more attention on the quality control are not included.

@@

\subsection{Trusted IoT Trading Infrastructure}
Multiple infrastructures for trusted IoT data trading have been proposed. Paolo Missier et. al\cite{MindMyValue} presented an IoT brokered infrastructure based marketplace which enables trading with Ethereum smart contracts. The brokers are only responsible for data transmission in order to adapt flexible agreement between participants. Unlike the standard pub/sub model that matches publishers and subscribers that participants are unaware of each other. However, the data cubes (i.e., a tuple of information, such as provider, subscriber and time period) are stored in a centralized Cassandra NoSQL database, referring as TrackerDB, is guarateed to be tamperproof but the risk of single point failure still exists.

\cite{TrustedMarketplaceWearable} focuses on trading the sensitive data among wearables. Several security issues are well discussed and solved with DLTs in the paper, the system consists multiple components that has its different responsibilities, such as data anonymizer eliminates keen information for privacy protection, access controller handles the key management and contract manager manages Ethereum smart contracts. While the trading processes are splited into multiple servers, and the request/response communication model is applied, the scalability problem of the marketplace remains.

In the following researches, IOTA MAM is regarded as a secure data storage which provides access control, tamperproof and authentication functionalities. IOTA is a DAG-based DLT that allows attaching zero value trasactions (i.e., messages) with no transaction fee, and MAM is a protocol that links the messages which forms a channel and endpoint. \cite{luDecentralizedDM} builds the data exchange system with MAM and IPFS, a content-based addressing distributed storage system. Considering the limited transaction processing capability of IOTA, the authors suggest to adopt IPFS to handle the encrypted large data sets, then add the encrypted IPFS link to MAM channel for further exchangement. This research focuses on secure data exchanging architecture design and security analysis, but the trading strategies are not studied yet.

In \cite{IOTASensorNode}, sensor nodes (SNs) in distributed sensor node system upload data to IOTA network via MAM protocol, and the Back-End server helps SNs to accelerate transaction attachments. The Back-End server also manages keys of data streams, record a tuple of SN, SN metadata, keys and available data stream entry points on MAM, and evaluates data price according to it's quality. Furthermore, as the Back-End server keeps all information of data products, it operates an user friendly interface of the marketplace and tackles all trading procedures. The heavy loading of Back-End server encounters the system scalability problem, single point failure as well as malicious attacks which may damage the profits of all players.

A similar approach to the previous one, the IOTA-based decentralized data marketplace in \cite{DDMSmartCities} puts data streams via MAM protocol as well. The data marketplace does not exist any intermediate server but data providers only, data providers generate and send data streams to MAM channel, and add a specific tag in transactions as an index that the marketplace application can retreive and show the product information on a map where data consumers can select from. Payments are in IOTA token with the transaction contains another type of tag, which both providers and consumers can double-check. Once the participants grows rapidly, this searching specific transactions by tags approach may fail due to the massive amount of transactions returned. Moreover, it is difficult to filter out the interested information and prevent adversaries spamming useless transactions.

\cite{SocialGood} proposed a smart transportation system that incorporate two DLTs, IOTA and Ethereum and a distributed storage IPFS. Though IOTA provides better scalability, it does not provide distributed computation as Ethereum smart contract. Thus, in this approach, IOTA and Ethereum are adopted to build a secure and smart system application, which is the principle we followed in our approach. Meanwhile, IPFS and MAM are viewed as the data storage in the system, where IPFS stores data that are not convenient to store on public chain and referenced to its hash into MAM transactions. Three types of MAM channels are used interactively to minimize the channel ID and key that data producers need to manage. However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from. Also, the details of trading are not illustrated in this paper.
